\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2015-11-27 tex/paper.tex
Reshuffled Models to be outside of implementation, again!

@@

\section{Related Work}
\subsection{Copy-on-Write}
This work relies heavily on the Copy-on-Write principle which was founded and used in the Mach
kernel~\cite{COPYONWRITE}.

@@

\newpage 
\section{Model}
\subsection{Entities}
%\subsubsection*{snapshot} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{Entity Relationships}
    \label{fig:relation}
\end{figure}

@@

ConcurrentHashMap had to be used in favour of the normal HashMap as the normal HashMaps can't be
iterated over concurrently.

@@

\newpage 
\section{Snapshots}
Write what snapshots are
\subsection{Copy-on-Write}
\label{sec:copy-on-write}
To efficiently create snapshots of a system Copy-on-Write can be used to make it possible to create
snapshots in O(1)\cite{BTRFS}, this is due to the fact that to create a snapshot in a system using
Copy-on-Write you only need to reference the current nodes in the tree and make sure that they are
not removed, see Figure~\ref{fig:btrfs_tree}.

@@

\subsection{Snapshots}
This implementation is far from as efficient as the other Copy-on-Write systems described in
Section~\ref{sec:copy-on-write} in most aspects, but more efficient in some. As the implementation
is built upon MongoDB as persistent storage and not a pure tree structure, single nodes can be
fetched in O(1) but when querying for subtrees they need to be built first, which takes O(log(n)),
where n is the number of nodes in the subtree.

In Perius snapshots and clones are not taken in the fashion which Btrfs uses, which can be seen in
Figure~\ref{fig:btrfs_tree}. As Perius does not have the tree structure pre-built and each node is
instead stored in a flat storage space, such operation would be too computationally expensive as
trees would have to be merged when collisions occur, due to the non-blocking nature of the
application. Instead this implementation makes a full copy of the meta-data of the tree, but still
refers to the same binary files until they are changed, which results in the creation of a new node.

>>>>

\subsection{Prior Work}
\subsubsection{Copy-on-Write}
This work relies heavily on the Copy-on-Write principle which was founded and used in the Mach
kernel~\cite{COPYONWRITE} as it can be used to efficiently create snapshots.

@@

\subsection{Terms}
\subsubsection{Snapshot}
A snapshot is a way to record the full state of a system at a specific time. The term comes from
photography where a photo can be seen as the state of what the photo is of at a certain time.
Snapshots should not be confused with full copies of a system as full copies can be used as backups
meanwhile snapshots are not very effective means of backups in the case of data corruption. It is
not effective against data corruption as snapshots usually still refer to unchanged data that is
still a part of the system~\cite{SNAPSHOT}.

@@

\newpage

\section{Model}
The model for this work should make sure that data can not be accessed by unauthorized users in the
Perius system (See section TODO: fill in). There could also be another model done to make sure that
content can not be accessed by unauthorized viewers once the content is uploaded to the CDN, but as
that should already have been thoroughly checked by the CDN providers this work can focus on the
internal users of the management system.

\subsection{Entities}
%\subsubsection*{snapshot} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{High Level Entity Relationships}
    \label{fig:relation}
\end{figure}

@@

ConcurrentHashMap had to be used in instead of the normal HashMap, as the normal HashMaps can't be
iterated over concurrently.

@@

\section{Snapshot systems}
\subsection{Copy-on-Write}
\label{sec:copy-on-write}
To efficiently create snapshots of a system Copy-on-Write can be used to make it possible to create
snapshots in O(1)\cite{BTRFS}, this is due to the fact that to create a snapshot in a system using
Copy-on-Write you only need to reference the current nodes in the tree and make sure that they are
not removed, see Figure~\ref{fig:btrfs_tree}.

@@

\subsection{Snapshot functionality}
In Perius snapshots and clones are not taken in the fashion which Btrfs uses, which can be seen in
Figure~\ref{fig:btrfs_tree}. As Perius does not have the tree structure pre-built and each node is
instead stored in a flat storage space, such operation would be too computationally expensive as
trees would have to be merged when collisions occur, due to the non-blocking nature of the
application. Instead this implementation makes a full copy of the meta-data of the tree, but still
refers to the same binary files until they are changed, which results in the creation of a new node.
